draft_final_assignment

### 2022-11-30 draft_final_assingment.Rmd
push rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
library(tidyr)
library(tidymodels) 
library(textrecipes)
library(plotly)
```

@@

```{r, wa }
dfmat_115 <- dfm_subset(dfmat, session == 115)

@@

```{r, wa }
dfmat_116 <- dfm_subset(dfmat, session == 116)

@@

```{r, wa }
dfmat_117 <- dfm_subset(dfmat, session == 117)

@@

## Wordcloud comparing Democrats and Republicans
```{r, wa }
dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups =
                     corp$party) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

@@

```{r, wa }

@@

## Wordcloud comparing Congresses
```{r, wa }
dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

@@

## Most common words (overall)
```{r, warning=FALSE}
#Overall most common words

@@

```{r, warning=FALSE}
#Republicans
dfmat_r <- dfm_subset(dfmat, party == "Republican")

@@

```{r, warning=FALSE}
#Democrats
dfmat_d <- dfm_subset(dfmat, party == "Democrat")

@@

```{r, warning=FALSE}
party_corp <- corpus_subset(corp, 
                            party %in% c("Democrat", "Republican"))

@@

```{r, warning=FALSE}
# Most common words by Congressional session 115
tfreq_115 <- dfmat_115 %>%
  textstat_frequency() %>%
  head(20)

@@

```{r, warning=FALSE}
# Most common words by Congressional session 116
tfreq_116 <- dfmat_116 %>%
  textstat_frequency() %>%
  head(20)

@@

```{r, warning=FALSE}
# Most common words by Congressional session 117
tfreq_117 <- dfmat_117 %>%
  textstat_frequency() %>%
  head(20)

@@

## Comparing subgroups
```{r, warning=FALSE}
df <- df %>%
  mutate(session_written = ifelse(session == 115, "session_115", 
                             ifelse(session == 116, "session_116",
                             ifelse(session == 117, "session_117", NA))))

@@

>>>>

```{r setup, warning=FALSE, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(quanteda)
library(quanteda.textstats)
library(readr)
library(dplyr)
library(quanteda.textplots)
library(uwot)
library(topicmodels)
library(tidytext)
library(ggrepel)
library(vader)
library(tidyr)
library(tidymodels) 
library(textrecipes)
library(plotly)
library(reticulate)
use_python("tad_venv3\\Scripts\\python.exe")
```

@@

```{r}
dfmat_115 <- dfm_subset(dfmat, session == 115)

@@

```{r}
dfmat_116 <- dfm_subset(dfmat, session == 116)

@@

```{r}
dfmat_117 <- dfm_subset(dfmat, session == 117)

@@

## Wordcloud comparing Democrats and Republicans
```{r}
dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups =
                     corp$party) %>%
  dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

@@

```{r}

@@

## Wordcloud comparing Congresses
```{r}
dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

@@

## Most common words (overall)
```{r}
#Overall most common words

@@

```{r}
#Republicans
dfmat_r <- dfm_subset(dfmat, party == "Republican")

@@

```{r}
#Democrats
dfmat_d <- dfm_subset(dfmat, party == "Democrat")

@@

```{r}
party_corp <- corpus_subset(corp, 
                            party %in% c("Democrat", "Republican"))

@@

```{r}
# Most common words by Congressional session 115
tfreq_115 <- dfmat_115 %>%
  textstat_frequency() %>%
  head(20)

@@

```{r}
# Most common words by Congressional session 116
tfreq_116 <- dfmat_116 %>%
  textstat_frequency() %>%
  head(20)

@@

```{r}
# Most common words by Congressional session 117
tfreq_117 <- dfmat_117 %>%
  textstat_frequency() %>%
  head(20)

@@

## Comparing subgroups
```{r}
df <- df %>%
  mutate(session_written = ifelse(session == 115, "session_115", 
                             ifelse(session == 116, "session_116",
                             ifelse(session == 117, "session_117", NA))))

@@

```{python}
import plotly.io as pio
fig = pio.read_json('slides\\plots\\polar_line_plot')
fig.show()
```
